---
title: "colorange"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{colorange}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The colorange package creates different corportate color palettes for your plots. It includes two functions `scale_color_orange()` and `scale_fill_orange()` that you can use with the ggplot2 package.
<br>
<br>
Colors and palettes respect the corporate identity and style guide of Orange™. See https://www.ateliers-orange.fr/index.php?page=marque for more details.

```{r, echo=FALSE}
library("colorange")
```

## Palette choice

The package contains height palettes.

```{r}
names(list_orange_palettes)
```

<br>
To display all of them at once, you can use the `display_orange_all()` function.
```{r, fig.width=7, fig.height=7, fig.align="center"}
display_orange_all()
```

<br>
If you want to see one particular palette, use the `display_orange_palette()` function.

```{r, fig.width=7, fig.height=5, fig.align="center"}
display_orange_palette("main")
```

<br>
Interpolation is usefull when you need more colors than the number available in the palette.

For instance, we can interpolate the "bleus" palette which originally includes three colors to a length of 10.

```{r, fig.width=7, fig.height=5, fig.align="center"}
display_orange_palette("blue", n = 10)
```

## Usage

There are two main ways of using the colors and palettes of the package:

- manually
- or with the help of the `scale_color_orange()` and `scale_fill_orange()` functions.

If you are going the first route, choose a color and specify it as always in the corresponding layer.
You can access the hexadecimal code of a color with the `orange_colors()` function.

```{r, fig.width=7, fig.height=5, fig.align="center"}
library("ggplot2")

ggplot(mtcars, aes(hp, mpg)) +
  geom_point(color = orange_colors("green"), size = 4, alpha = .8) +
  theme_minimal()
```

<br>
Using the `scale_color_orange()` and `scale_fill_orange()` functions is as simple.

With `scale_color_orange()`:

```{r, fig.width=7, fig.height=5, fig.align="center"}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_orange(palette = "secondary", discrete = TRUE) +
  theme_minimal()
```

<br>
And with `scale_fill_orange()`:

```{r, fig.width=7, fig.height=5, fig.align="center"}
ggplot(mpg, aes(x = fl, y = displ, fill = fl)) +
  geom_boxplot() +
  scale_fill_orange(palette = "secondary", guide = "none") +
  theme_minimal()
```
